Fitbit & ET Glasses - Methods

### 2023-10-10 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
update blabla

---
title: "Fitbit & ET Glasses - Methods"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      psych,
      stargazer,
      lmtest,
      sandwich,
      car)

@@

@@

>>>>

---
title: "Fitbit & ET Glasses - Methods"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Packages
# install.packages("needs")
# Choose "No"
library(needs)
needs(tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      psych,
      stargazer,
      lmtest,
      sandwich,
      car,
      stats)

@@

# check for normality assumption --> can be checked by computing Shapiro-Wilk test for each time point. If the data is normally distributed, the p-value should be greater than 0.05
norm_assump <-
  df_anova %>%
  group_by(time_span) %>%
  shapiro_test(mean_hr_std)

@@

# effektstärke für ANOVA
DescTools::EtaSq(df_anova_phase)
f = sqrt (0.7202944/ (1-0.7202944))

# geplante Kontraste
model <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
summary (model)

contrast1 <- c(-1, 1, 0, 0, 0)
contrast2 <- c(0, 1, -1, 0, 0)
contrast3 <- c(0, 1, 0, -1, 0)
contrast4 <- c(0, 1, 0, 0, -1)

contrasts(df_anova_subset$time_span) <- cbind(contrast1,
                                              contrast2,
                                              contrast3,
                                              contrast4)

model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
summary(model2)

summary.aov(model2, 
            split = list (time_span = list ("Lehrphase vs. Pre-Lehrphase" = 1,
                                            "Lehrphase vs. Post-Lehrphase" = 2,
                                            "Lehrphase vs. Interviewphase" = 3,
                                            "Lehrphase vs. Endphase" = 4
                                            )
                          )
            )
